---
title: "Lab 00 - Hello IDS!"
author: "JESSIE"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Jessie Preston", "member 1", "member 2", 
           "member 3", "member 4"),
  github_username = c("jessiepreston", "username 1", "username 2", 
                      "username 3", "username 4"), 
  colour = c("orchid", "wheat", "slategray3", 
             "sienna", "seagreen2"),
  hobby = c("Hopping", "running", "painting", 
            "walking", "shopping"),
  favourite_number = c(2, 3, 10, 1, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A bar graph visually depicting each members favourite number and colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "favourite_number",
          title = "Team_Members_Info")
```

The labs() command modifies axis and title in bar plot

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
